Homework_2

### 2022-09-06 hw2/anshit/Homework_2.Rmd
added box plots for analysis

```{r}
iris_data = read.table('./iris.txt', header = TRUE, sep='', dec='.')
head(iris_data)
dim(iris_data)
```

@@

```{r}
# Calculation of best 'K'
elbow_graph_data <- data.frame(K=integer(), sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  elbow_graph_data[nrow(elbow_graph_data) + 1, ] = c(k, km.res$tot.withinss)
}
```

@@

```{r}
plot(elbow_graph_data, type='b', ylab='Total Sum of Square Within', main='Elbow Graph', )
```

@@

```{r}
best_km <- kmeans(as.matrix(scale(iris_data[,1:4])), 3, nstart = 25)
best_km
```

@@

```{r}
best_km$centers
```

>>>>

```{r}
iris_data = read.table('./iris.txt', header = TRUE, sep='', dec='.')
head(iris_data,50)
dim(iris_data)
```

@@

```{r}
# Calculation of best 'K'
elbow_graph_data <- data.frame(K=integer(), within_sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  elbow_graph_data[nrow(elbow_graph_data) + 1, ] = c(k, km.res$tot.withinss)
}
```

@@

```{r}
plot(elbow_graph_data, type='b', ylab='Total Sum of Square Within', main='Elbow Graph', col='blue')
```
```{r}
# Calculation of best 'K'
bw_graph_data <- data.frame(K=integer(), between_sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  bw_graph_data[nrow(bw_graph_data) + 1, ] = c(k, round(km.res$betweenss,2))
}
#options(scipen=999)
bw_graph_data
```

```{r}
plot(bw_graph_data, type='b', ylab='Betweeen Sum of Square (Intra Cluster)', main='BW SS Graph', col='green')
```

```{r}
# Calculation of best 'K'
ratio_graph_data <- data.frame(K=integer(), ratio=double())
for(k in seq(2, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  ratio_graph_data[nrow(ratio_graph_data) + 1, ] = c(k, round(km.res$tot.withinss/km.res$betweenss,2))
}
#options(scipen=999)
ratio_graph_data
```
```{r}
plot(ratio_graph_data, type='b', ylab='Ratio Within/Between SS', main='Quality', col='red')
```

@@

```{r}
best_km <- kmeans(as.matrix(scale(iris_data[,1:4])), 3, nstart = 25)
out<-cbind(iris_data,tagged_cluster=best_km$cluster)
out
```
```{r}
boxplot(Sepal.Length~tagged_cluster,data=out)
```

```{r}
out$tagged_cluster<-as.factor(out$tagged_cluster)
ggplot(out, aes(x=tagged_cluster, y=Sepal.Length,fill=tagged_cluster)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

out$tagged_cluster<-as.factor(out$tagged_cluster)
ggplot(out, aes(x=tagged_cluster, y=Sepal.Width,fill=tagged_cluster)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

out$tagged_cluster<-as.factor(out$tagged_cluster)
ggplot(out, aes(x=tagged_cluster, y=Petal.Length,fill=tagged_cluster)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

out$tagged_cluster<-as.factor(out$tagged_cluster)
ggplot(out, aes(x=tagged_cluster, y=Petal.Width,fill=tagged_cluster)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")
```
Petal width and Petal Length are strong indicators for one class (setosa)

@@

```{r}
# function getStatusForClusterAndSpecie(row){
#   if(row$tagged_cluster=="1" & row$Species=="versicolor"){'improper_versicolor'}
#   else if(row$tagged_cluster=="2" & row$Species=="virginica"){'improper_virginica'}
#   else if()
#   
# }
```

```{r}
classifier_df = out[!out$Species=='setosa',]
classifier_df$status = ''
classifier_df$status[(classifier_df$tagged_cluster=="1" & classifier_df$Species=="versicolor")] = 'improper_versicolor'
classifier_df$status[(classifier_df$tagged_cluster=="2" & classifier_df$Species=="virginica")] = 'improper_virginica'
classifier_df$status[(classifier_df$tagged_cluster=="2" & classifier_df$Species=="versicolor")] = 'proper_versicolor'
classifier_df$status[(classifier_df$tagged_cluster=="1" & classifier_df$Species=="virginica")] = 'proper_virginica'

classifier_df

```
```{r}
classifier_df$status<-as.factor(classifier_df$status)
ggplot(classifier_df, aes(x=status, y=Sepal.Length,fill=status)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

ggplot(classifier_df, aes(x=status, y=Sepal.Width,fill=status)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

ggplot(classifier_df, aes(x=status, y=Petal.Length,fill=status)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")

ggplot(classifier_df, aes(x=status, y=Petal.Width,fill=status)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")
```

```{r}
out$tagged_cluster<-as.factor(out$tagged_cluster)
ggplot(out, aes(x=tagged_cluster, y=Petal.Width,fill=tagged_cluster)) + geom_boxplot(alpha=0.3) +theme(legend.position="none")
```
